---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maggieliu545ba2

<!-- badges: start -->
<!-- badges: end -->

This package provides a function `plot_hist_with_density` that plots a histogram of a column from a specified dataset, and a smooth density curve overlayed on the histogram. The function allows for customizable parameters for visualization.

## Installation

You can install `maggieliu545ba2` using

```
devtools::install_github("stat545ubc-2021/maggieliu545ba2")
```

and load the package with

```
library("maggieliu545ba2")
```

## Example
Below is an example of using the function `plot_hist_with_density`:
```{r}
library(maggieliu545ba2)
(plot_hist_with_density(
  data=iris,
  column=Sepal.Length,
  xlab="Sepal Length",
  title="Histogram and density plot of sepal length"))
```
